---
title: "PPE Performance Report"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(scales)
library(here)
library(ggplot2)
library(data.table)
library(patchwork)

source(here("current", "plots", "age_stratified_estimate_plots", "bias_age_strata.R"))
source(here("current", "plots", "age_stratified_estimate_plots", "ecr_age_strata.R"))
source(here("current", "plots", "age_stratified_estimate_plots", "mean_se_age_strata.R"))
source(here("current", "plots", "age_stratified_estimate_plots", "estimate_sd_age_strata.R"))
source(here("current", "plots", "age_stratified_estimate_plots", "variance_calibration_age_strata.R"))
source(here("current", "plots", "age_stratified_estimate_plots", "cancer_deaths_age_strata.R"))

# Cumulative Representations by Age Strata(proportion)
source(here("current", "plots", "final_report", "cum_cancer_prop_age_strata.R"))
source(here("current", "plots", "final_report", "n_at_risk_prop_age_strata.R"))
source(here("current", "plots", "final_report", "cum_total_deaths_prop_age_strata.R"))
source(here("current", "plots", "final_report", "cum_other_prop_age_strata.R"))

## # Cumulative Representations by Age Strata (absolute)
source(here("current", "plots", "final_report", "cum_cancer_age_strata.R"))
source(here("current", "plots", "final_report", "n_at_risk_age_strata.R"))
source(here("current", "plots", "final_report", "cum_total_deaths_age_strata.R"))
source(here("current", "plots", "final_report", "cum_other_age_strata.R"))

# Other plots
source(here("current", "plots", "age_stratified_estimate_plots", "sd_risk_age_strata.R"))
source(here("current", "plots", "age_stratified_estimate_plots", "PPviz_parallel_function_age_strata.R"))
source(here("current", "plots", "plot_hypothesis.R"))



# 1. Specify a vector of target lambda scenarios
target_lambdas <- c(0.1) 

# read data
results_df <- read_csv(here("current", "outputs", "tables", "final_results_complete.csv")) %>%
  dplyr::mutate(lambda = as.numeric(lambda))
#data_plot <- readRDS(here("current", "outputs", "tables", #"final_weight_distribution_analysis.rds"))
#setDT(data_plot)

# Isolate the older patient stratum (>=65) at the 7-year horizon
#df_7yr_older <- data_plot[horizon_years == 7 & pp_age_class == ">=65"]


batch_code <- readLines(here("current", "main_batch.R"))

get_param <- function(param_name, code = batch_code) {
  line <- code[str_detect(code, paste0("^", param_name, "\\s*<-"))]
  if(length(line) > 0) {
    # Extract everything after <- and strip comments/whitespace
    val <- str_match(line, paste0("^", param_name, "\\s*<-\\s*([^#]+)"))[2]
    return(str_trim(val))
  }
  return("Not found")
}

# Store parameters in a list
params_list <- list(
  n_patients     = get_param("n_patients"),
  age_option     = get_param("age_option"),
  beta_age       = get_param("beta_age"),
  beta_sex       = get_param("beta_sex"),
  year_min       = get_param("year.start_min"),
  year_max       = get_param("year.start_max"),
  prop_female    = get_param("prop_female"),
  N_files        = get_param("N_files"),
  max_time       = get_param("max_time")
)

```
## Simulation Configuration

> **Note:** This report reflects the performance metrics evaluated for the following simulation configuration:

* **Number of Patients ($N$):** `r params_list$n_patients`
* **Simulated Cohorts (Files):** `r params_list$N_files`
* **Follow-up Cutoff (Years):** `r params_list$max_time` years
* **Age Distribution Cohort:** `r params_list$age_option`
* **Beta Coefficients:** * Age ($\beta_{age}$): `r params_list$beta_age`
    * Sex ($\beta_{sex}$): `r params_list$beta_sex`
* **Inclusion Window:** `r params_list$year_min` to `r params_list$year_max`
* **Female Proportion:** `r params_list$prop_female`

```{r}
plot_bias_by_age(
  results_df   = results_df,
  title        = "PPE Bias Under Competing Risks by Age Class",
  followup_lab = "Follow-up"
)

#print(bias_plot)
```

```{r}
plot_ecr_by_age(
  results_df   = results_df,
  title        = "PPE ECR Under Competing Risks by Age Class",
  followup_lab = "Follow-up"
)

#print(bias_plot)
```

```{r}
plot_mean_se_by_age(
  results_df   = results_df,
  title        = "PPE Mean Estimated SE Under Competing Risks by Age Class",
  followup_lab = "Follow-up"
)
```

```{r}
plot_estimate_sd_by_age(
  results_df   = results_df,
  title        = "PPE Empirical Dispersion (Estimate SD) Under Competing Risks by Age Class",
  followup_lab = "Follow-up"
)
```

```{r}
# plot_se_calibration_ratio_by_age(
#   results_df   = results_df,
#   title        = "PPE Empirical Dispersion (Estimate SD) Under Competing Risks by Age Class",
#   followup_lab = "Follow-up"
# )
```

## Pohar-Perme Visualization by Lambda Scenario age strata-specific overlay

```{r}
#| label: ppviz-age-strata-precompute
#| include: false

save_dir <- here("current", "outputs", "plots_data_age_strata")

# Build exact filenames without padding
target_filenames <- paste0("ppviz_age_strata_lambda_", as.character(target_lambdas), ".rds")
target_file_paths <- file.path(save_dir, target_filenames)

missing_files <- target_lambdas[!file.exists(target_file_paths)]

if (length(missing_files) > 0) {
  message("Pre-computed plots missing for lambdas: ", paste(missing_files, collapse = ", "), ". Running pre-computation...")
  
  results_df <- results_df %>% 
    dplyr::filter(lambda %in% target_lambdas)
  
  source(here("current", "plots", "age_stratified_estimate_plots", "precompute_viz_data_age_strata.R")) 
} else {
  message("Pre-computed data for all targeted lambdas already exists. Skipping pre-computation step.")
}
```

```{r}
#| label: fig-ppviz-age-strata-multiple-lambdas
#| fig.width: 9
#| fig.height: 6
#| fig.cap: "Age-Stratified Pohar-Perme versus theoretical net survival for selected lambda scenarios."
#| layout-ncol: 1

# 4. Loop through the specific file paths you defined above
for (file_path in target_file_paths) {
  if (!file.exists(file_path)) {
    warning("Warning: Pre-computed .rds plot file not found at ", file_path)
    next # Skip to the next file if one is somehow missing
  }
  
  p_data <- readRDS(file_path)
  
  # Extract and print the ggplot object
  print(p_data$plot_obj)
}
```


## Cumulative Representations by Age Strata
```{r}
plot_cum_cancer_prop_by_age(results_df)
```

```{r}
plot_cum_cancer_by_age(results_df)
```

```{r}
plot_n_at_risk_prop_by_age(results_df)
```

```{r}
plot_n_at_risk_by_age(results_df)
```

```{r}
plot_cum_total_deaths_prop_by_age(results_df)
```

```{r}
plot_cum_total_deaths_by_age(results_df)
```

```{r}
plot_cum_other_prop_by_age(results_df)
```

```{r}
plot_cum_other_by_age(results_df)
```
)

## Empirical SD vs Number at Risk
```{r}
plot_sd_vs_risk_age_strata(results_df)
```

## Case 1: Weights and Risk-Set Size

```{r}
#| fig-width: 9
#| fig-height: 12
# Calls function and renders directly in document; saves PNG
# plot_case1_weights_and_riskset(
#   data = data_plot,
#   target_horizon = 7,
#   target_age_class = ">=65",
#   save_path = here("current", "outputs", "plot_case1_weights_and_riskset.png")
# )
```

## Case 2: Survivor Age Profiles

```{r}
# plot_case2_survivor_age_profiles(
#   data = data_plot,
#   target_horizon = 7,
#   target_age_class = ">=65",
#   save_path = here("current", "outputs", "plot_case2_survivor_age_percentiles.png")
# )
```
