---
title: "PPE Performance Report"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(scales)
library(here)

# Source plotting functions using project-root absolute paths
source(here("current", "plots", "ecr_graph_function.R"))
source(here("current", "plots", "absolute_bias_graph_function.R"))
source(here("current", "plots", "bias_graph_function.R"))
source(here("current", "plots", "rmse_graph_function.R"))
source(here("current", "plots", "PPviz_parallel_function.R"))
source(here("current", "plots", "estimate_sd_graph_function.R"))
source(here("current", "plots", "estimation_error_sd_graph_function.R"))
source(here("current", "plots", "mean_se_graph_function.R"))
source(here("current", "plots", "variance_calibration_graph_function.R"))

results_df <- read_csv(here("current", "outputs", "tables", "final_results_complete.csv"))

save_dir <- here("current", "outputs", "plots_data")

# Extract global parameters dynamically from main_batch.R
batch_code <- readLines(here("current", "main_batch.R"))

get_param <- function(param_name, code = batch_code) {
  line <- code[str_detect(code, paste0("^", param_name, "\\s*<-"))]
  if(length(line) > 0) {
    # Extract everything after <- and strip comments/whitespace
    val <- str_match(line, paste0("^", param_name, "\\s*<-\\s*([^#]+)"))[2]
    return(str_trim(val))
  }
  return("Not found")
}

# Store parameters in a list
params_list <- list(
  n_patients     = get_param("n_patients"),
  age_option     = get_param("age_option"),
  beta_age       = get_param("beta_age"),
  beta_sex       = get_param("beta_sex"),
  year_min       = get_param("year.start_min"),
  year_max       = get_param("year.start_max"),
  prop_female    = get_param("prop_female"),
  N_files        = get_param("N_files"),
  max_time       = get_param("max_time")
)

# Check if the generated data already exists
generated_files <- list.files(save_dir, pattern = "^ppviz_data_lambda_.*\\.rds$")

if (length(generated_files) == 0) {
  message("Pre-computed plots not found. Running parallel pre-computation...")
  source(here("current", "plots", "precompute_viz_data.R")) 
} else {
  message("Pre-computed data already exists. Skipping pre-computation step.")
}
```
## Simulation Configuration

> **Note:** This report reflects the performance metrics evaluated for the following simulation configuration:

* **Number of Patients ($N$):** `r params_list$n_patients`
* **Simulated Cohorts (Files):** `r params_list$N_files`
* **Follow-up Cutoff (Years):** `r params_list$max_time` years
* **Age Distribution Cohort:** `r params_list$age_option`
* **Beta Coefficients:** * Age ($\beta_{age}$): `r params_list$beta_age`
    * Sex ($\beta_{sex}$): `r params_list$beta_sex`
* **Inclusion Window:** `r params_list$year_min` to `r params_list$year_max`
* **Female Proportion:** `r params_list$prop_female`

## Empirical Coverage

```{r fig-ecr-coverage, fig.width=9, fig.height=6, fig.cap="PPE empirical coverage under competing risks."}
plot_ecr(results_df)
```


## Absolute Bias

```{r fig-absolute-bias, fig.width=9, fig.height=6, fig.cap="PPE bias under competing risks."}
plot_absolute_bias(results_df)
```


## Bias

```{r fig-bias, fig.width=9, fig.height=6, fig.cap="PPE bias under competing risks."}
plot_bias(results_df)
```


## Root Mean Square Error

```{r fig-rmse, fig.width=9, fig.height=6, fig.cap="PPE root mean square error under competing risks."}
plot_rmse(results_df)
```

## Variance

```{r fig-dispersion, fig.width=9, fig.height=6, fig.cap="PPE empirical dispersion under competing risks."}
plot_estimate_sd(results_df)
```
```{r fig-estimation-error, fig.width=9, fig.height=6, fig.cap="PPE empirical dispersion under competing risks."}
plot_estimation_error_sd(results_df)
```

```{r fig-mean-sd, fig.width=9, fig.height=6, fig.cap="PPE mean estimated standard error under competing risks."}
plot_mean_se(results_df)
```

```{r fig-variance-calibration, fig.width=9, fig.height=6, fig.cap="Ratio of mean model estimated SE to empirical SD of the estimation error (bias)"}
plot_variance_calibration(results_df)
```

## Pohar-Perme Visualization by Lambda Scenario

```{r fig-ppviz-all-lambdas, fig.width=9, fig.height=6, fig.cap="Pohar-Perme versus theoretical net survival by lambda scenario.", echo=FALSE}
#| layout-ncol: 1

target_dir <- here("current", "outputs", "plots_data")

plot_files <- sort(list.files(target_dir, pattern = "^ppviz_data_lambda_.*\\.rds$", full.names = TRUE))

if (length(plot_files) == 0) {
  stop("Error: No pre-computed .rds plot files found in ", target_dir)
}

for (p_file in plot_files) {
  p <- readRDS(p_file)
  
  plot(
    0, type = "n", xlim = c(0, max(p$t_seq_years)), ylim = c(0.8, 1.0),
    xlab = "Time since diagnosis (Years)", ylab = "Net Survival Probability",
    main = paste0("Net Survival: PP vs Theoretical\nLambda = ", sprintf("%.4f", p$lambda), 
                  "; Proportion of deaths due to cancer: ", p$pct_cancer, "%")
  )
  grid()
  
  # Plot individual sampled runs
  n_cols <- ncol(p$pp_surv_matrix)
  sampled_cols <- sample(seq_len(n_cols), size = min(20, n_cols))
  for (i in sampled_cols) {
    lines(p$t_seq_years, p$pp_surv_matrix[, i], col = rgb(0.2, 0.5, 0.8, alpha = 0.3), lwd = 1, type = "s")
  }
  
  # Plot mean and theoretical curves
  lines(p$t_seq_years, p$mean_pp_surv, col = "red", lwd = 3, type = "l")
  lines(p$t_seq_years, p$surv_theo_mean, col = "black", lwd = 3, lty = 2)
  
  legend("bottomleft",
    legend = c(paste0("Individual PP Estimates (N = ", length(sampled_cols), ")"),
               "Mean PP Estimate", "Theoretical Net Survival Curve S(t)"),
    col = c(rgb(0.2, 0.5, 0.8, alpha = 0.5), "red", "black"),
    lwd = c(2, 3, 3), lty = c(1, 1, 2), bty = "n", cex = 0.85
  )
}
```