---
title: "PPE Performance Report"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(scales)
library(here)

source(here("current", "plots", "risk_set_diagnostics", "composition.R"))

results_df <- read_csv(here("current", "outputs", "tables", "final_results_complete.csv"))

metrics <- readRDS(here("current", "outputs", "tables", "final_results_complete.rds"))

# Extract global parameters dynamically from main_batch.R
batch_code <- readLines(here("current", "main_batch.R"))

get_param <- function(param_name, code = batch_code) {
  line <- code[str_detect(code, paste0("^", param_name, "\\s*<-"))]
  if(length(line) > 0) {
    # Extract everything after <- and strip comments/whitespace
    val <- str_match(line, paste0("^", param_name, "\\s*<-\\s*([^#]+)"))[2]
    return(str_trim(val))
  }
  return("Not found")
}

# Store parameters in a list
params_list <- list(
  n_patients     = get_param("n_patients"),
  age_option     = get_param("age_option"),
  beta_age       = get_param("beta_age"),
  beta_sex       = get_param("beta_sex"),
  year_min       = get_param("year.start_min"),
  year_max       = get_param("year.start_max"),
  prop_female    = get_param("prop_female"),
  N_files        = get_param("N_files"),
  max_time       = get_param("max_time")
)
```

## Simulation Configuration

> **Note:** This report reflects risk-set diagnostics to check whether variability comes from effective sample size issues.

* **Number of Patients ($N$):** `r params_list$n_patients`
* **Simulated Cohorts (Files):** `r params_list$N_files`
* **Follow-up Cutoff (Years):** `r params_list$max_time` years
* **Age Distribution Cohort:** `r params_list$age_option`
* **Beta Coefficients:** * Age ($\beta_{age}$): `r params_list$beta_age`
    * Sex ($\beta_{sex}$): `r params_list$beta_sex`
* **Inclusion Window:** `r params_list$year_min` to `r params_list$year_max`
* **Female Proportion:** `r params_list$prop_female`

## Cohort Composition across pct_cancer (Stacked Bar Chart)

```{r fig-cohort-comp, fig.width=9, fig.height=6}
plot_composition(results_df)
```
